---
title: 'R Notebook: intro'
author: "Antonio D. Barber [antonio_barber]"
output:
  html_document:
    df_print: paged
---


```{r}
# github.monte
which.github = "local";  # local ... remote 

github.local = "C:/_git_/github/TEMPLATE-Pseudo/";
github.remote = "https://raw..../";

if(which.github == "remote")
  {
  include.me = paste0( github.remote, "functions/functions-intro.R");
  library(devtools);
  source_url(include.me);
  } else {
          include.me = paste0( github.local, "functions/functions-intro.R");
          source(include.me);
          }
```

```{r}
(library(plotrix))
```

# Handshake
Displaying the Handshake function
```{r}
handShake(5)
```
## Function Parameters
Displaying the Handshake function with a parameter of 6, 7, 8, 9, 10
```{r}
handShake(6)
handShake(7)
handShake(8)
handShake(9)
handShake(10)
```

## Calculation of plotMe
```{r}
handShake(5, plotMe = TRUE)
```


# Alphabet Declaration of Independence
The letter count of the original draft.(Thomas Jefferson draft)
```{r my-chunk, R.options = list(width = 1000)}

letter_counter(read_orginal())
```

The letter count of the unanimous draft.(The draft signed by Congress)
```{r my-chunk2, R.options = list(width = 1000)}

letter_counter(read_unanimous())
```

The letter count of combining both drafts.
```{r my-chunk3, R.options = list(width = 1000)}
letter_counter(combine_drafts())
```


# Determinant of 3x3 matrix
 The formula for finding the determinant of a matrix is:
$$ det(A) = |A|=
\left[\begin{array}{cc} 
a & b & c\\ 
d & e & f\\
g & h & i
\end{array}\right] 
= a\left[\begin{array}{cc} 
e & f \\ 
h & i \\
\end{array}\right] 
- b\left[\begin{array}{cc} 
d & f \\ 
g & i \\
\end{array}\right] 
- c\left[\begin{array}{cc} 
d & e \\ 
g & h \\
\end{array}\right] 
\\= a(ei - fh) - b(di - gf) + c(dh -eg) \\
= aei + bfg + cdh - ceg -afh -dbi
$$ 
Lets define matrix B as:
$$ B =
\left[\begin{array}{cc} 
6 & 1 & 1\\ 
4 & -2 & 5\\
2 & 8 & 7
\end{array}\right] 
$$
Using the function computeDeterminant to compute the determinant of matrix B:

```{r}
matrix1 <- matrix(c(6, 4, 2, 1, -2, 8, 1, 5, 7), nrow = 3)
print(matrix1)
computeDeterminant(matrix1)
```


We will now check the results of computeDeterminant, Observe:
$$ det(B) = |B|=
\left[\begin{array}{cc} 
6 & 1 & 1\\ 
4 & -2 & 5\\
2 & 8 & 7
\end{array}\right] 
= 6\left[\begin{array}{cc} 
-2 & 5 \\ 
8 & 7 \\
\end{array}\right] 
- 1\left[\begin{array}{cc} 
4 & 5 \\ 
2 & 7 \\
\end{array}\right] 
- 1\left[\begin{array}{cc} 
4 & -2 \\ 
2 & 8 \\
\end{array}\right] 
\\= 6((-2*7) - (5*8)) - 1((4*7) - (2*5)) + 1((4*8) -(-2*2)) \\
= (6*-54) - (1*18) + 1(36))\\
det(B)=-306
$$ 
